
\newpage
\thispagestyle{plain}
\begin{center}

    \vspace*{0.1cm}
    \Large
    \textbf{Acknowledgements}\\
    \vspace{0.5cm}

\end{center}

First of all, we would like to express our sincere gratitude to Almighty Allah for giving us the strength, patience, and ability to complete this project successfully.

We would like to express our deepest gratitude to our respected course instructor, \textbf{Dr. Nazmun Nahid}, Assistant Professor, Department of Computer Science and Engineering, University of Asia Pacific, for her valuable guidance, support, and encouragement throughout the development of this project. Her instructions and suggestions helped us understand the project requirements and complete the work in a proper and organized way.

We are also thankful to the Department of Computer Science and Engineering, University of Asia Pacific, for providing us with the opportunity to work on this robotics lab project. The knowledge gained from the course helped us apply concepts of robotics, embedded systems, sensors, actuators, and IoT communication in a practical project.

We would like to thank our group members for their cooperation, teamwork, and dedication during the planning, hardware setup, coding, testing, and report writing stages of the project. The successful completion of the \textbf{Automated Car Parking System} was possible because of the combined effort of all team members.

Finally, we are grateful to our families and friends for their continuous support, motivation, and encouragement throughout the project work.

